Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Streamline cjb's learning style example.

Other rule groups may invoke random selection, select between stories
based on child preferences or curriculum (for example, the system
could attempt to learn a child's preference for verbal vs. visual
learning), or (during development) flag an error to highlight an
unexpected ambiguity.

>>>>

Other rule groups may invoke random selection, select between stories
based on child preferences, curriculum, or inferred learning style,
or (during development) flag an error to highlight an
unexpected ambiguity.
